---
title: "Exploratory Data Analysis Report"
output: html_document
params:
  data:
    value: data
---

```{r, echo=FALSE}
edadata <- params$data
head(edadata)
```

### Numeric Type

+ First Set of Descriptions Numeric Variables

```{r num_out1}
num_out <- num_summary(edadata)
cselect1 <- c(1:7)
knitr::kable(num_out[, cselect1, with = FALSE])
```

+ Second Set of Description for Numeric Variables

```{r num_out2}
num_out <- num_summary(edadata)
cselect2 <- c(1:3, 8:11)
knitr::kable(num_out[, cselect2, with = FALSE])
```

+ Third Set of Description for Numeric Variables

```{r num_out3}
num_out <- num_summary(edadata)
cselect3 <- c(1:3, 12:16)
knitr::kable(num_out[, cselect3, with = FALSE])
```

+ Fourth Set of Description for Numeric Variables

```{r num_out4}
num_out <- num_summary(edadata)
cselect4 <- c(1:3, 17:20)
knitr::kable(num_out[, cselect4, with = FALSE])
```

### Character type

```{r char_out}
char_out <- char_summary(edadata)
knitr::kable(char_out)
```

### Date Type

+ Date Summary Part 1

```{r date_out}
date_out <- date_summary(edadata)
dselect1 <- c(1:7)
knitr::kable(date_out[, dselect1, with = FALSE])
```

+ Date Summary Part 2

```{r date_out2}
date_out <- date_summary(edadata)
dselect2 <- c(1:3, 8:10)
knitr::kable(date_out[, dselect2, with = FALSE])
```

### Logical type

```{r log_out}
log_out <- log_summary(edadata)
knitr::kable(log_out)
```

Since, there are no logical variable function returned the warning message and stopped.

### Factor Type

```{r fac_out}
fac_out <- factor_summary(edadata)
knitr::kable(fac_out)
```
