---
title: "Exploratory Data Analysis Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    code_download: TRUE
  word_document: default
  pdf_document: default
params:
  data:
    value: iris
---
## Versoning Report TimeStamp
Timestamp: `r Sys.time()`

```{r, echo=FALSE}
list_packages <- c("data.table", "knitr", "DT", "sparkline")
if (length(setdiff(list_packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(list_packages, rownames(installed.packages())))  
}
library(data.table)
library(expdata)
library(knitr)
library(DT)
library(sparkline)
edadata <- data.table(get(params$data))
```
## Data Summary
### Meta Data
```{r meta, echo=FALSE}
meta <- data.frame(Attribute = c("Num Columns", "Num Rowa"), Value = c(ncol(edadata), nrow(nrow(edadata))))
datatable(meta)
```

### Preview Data
```{r}
head(edadata)
```

### Numeric Type

+ First Set of Descriptions Numeric Variables

```{r num_out1, echo=FALSE}
num_out <- num_summary(edadata)
cselect1 <- c(1:7)
datatable(num_out[, cselect1, with = FALSE])
```

+ Second Set of Description for Numeric Variables

```{r num_out2, echo=FALSE}
num_out <- num_summary(edadata)
cselect2 <- c(1:3, 8:11)
datatable(num_out[, cselect2, with = FALSE])
```

+ Third Set of Description for Numeric Variables

```{r num_out3, echo=FALSE}
num_out <- num_summary(edadata)
cselect3 <- c(1:3, 12:16)
datatable(num_out[, cselect3, with = FALSE])
```

+ Fourth Set of Description for Numeric Variables

```{r num_out4, echo=FALSE}
num_out <- num_summary(edadata)
cselect4 <- c(1:3, 17:20)
datatable(num_out[, cselect4, with = FALSE])
```

### Character type

```{r char_out, echo=FALSE}
char_out <- char_summary(edadata)
datatable(char_out)
```

### Date Type

+ Date Summary Part 1

```{r date_out, echo=FALSE}
date_out <- date_summary(edadata)
dselect1 <- c(1:7)
datatable(date_out[, dselect1, with = FALSE])
```

+ Date Summary Part 2

```{r date_out2, echo=FALSE}
date_out <- date_summary(edadata)
dselect2 <- c(1:3, 8:10)
datatable(date_out[, dselect2, with = FALSE])
```

### Logical type

```{r log_out, echo=FALSE}
log_out <- log_summary(edadata)
datatable(log_out)
```

Since, there are no logical variable function returned the warning message and stopped.

### Factor Type

```{r fac_out, echo=FALSE}
fac_out <- factor_summary(edadata)
datatable(fac_out)
```

## Session Information
```{r ver, echo=FALSE}
sessionInfo()
```

